% !TEX root =main.tex

 %\vspace{-1mm}
\section{Conclusion and Future Research}\label{sec::conclusion}


An APP fraud takes place when fraudsters deceive a victim to make a payment to a bank account controlled by the fraudsters. Although APP frauds have been growing at a concerning rate, the  victims are not receiving a sufficient level of protection and the reimbursement rate is still low. Authorities and regulators have  provided guidelines  to prevent APP frauds occurrence and improve victims’ protection, but these guidelines are still vague and open to interpretation. In this work, to facilitate APP frauds victims’ reimbursement,  we proposed the notion of “Payment with Dispute Resolution” (PwDR). We identified a set of vital properties that a PwDR scheme should possess and formally defined them. Moreover,  we proposed a candidate construction and  studied its cost via asymptotic and concrete runtime evaluation. Our cost analysis indicated that the construction is efficient. 



Future research can investigate and identify key factors   that can improve the effectiveness of banks warnings that is one of the  key players in   lowering the rate of APP frauds occurrence.  Furthermore, with the increase in the popularity of  alternative payment platforms (e.g., CBDC or cryptocurrency), it is likely that  fraudsters will target their users. Hence, another interesting future research direction would be to design secure dispute resolution protocols  to protect  APP frauds victims in these platforms as well. 



